A general Nullstellensatz for generalized spaces

### 2019-03-17 paper-qcoh.tex
Review of basic facts about the classifying topos of Horn theories

Throughout this section, let~$\TT$ be a Horn theory.

@@

\begin{lemma}The category of~$\TT$-models is complete and
cocomplete.\end{lemma}

@@

% XXX Set[T] einführen

@@

% XXX terminology "U_T-algebra". location of the tensor explanation

>>>>

Throughout this section, let~$\TT$ be a Horn theory. It is a basic result that
Horn theories are of presheaf type, such that the classifying topos~$\Set[\TT]$
can be taken as the topos of functors~$\Mod{\TT}_\mathrm{fp} \to \Set$,
where~$\Mod{\TT}_\mathrm{fp}$ is the full subcategory of the category
of~$\TT$-models (in~$\Set$) on the finitely presentable objects. The
(underlying object of the) generic model is the tautologous functor~$U_\TT : T
\mapsto T$. By~\emph{$U_\TT$-algebra} we mean, in analogy with the terminology in
the case that~$\TT$ is the theory of rings, a~$\TT$-model~$M$ equipped with
a~$\TT$-homomorphism~$U_\TT \to M$.

@@

@@

\begin{lemma}The category of~$\TT$-models (in~$\Set$) is complete and
cocomplete.\end{lemma}

@@
